---
title: "Parameters estimation for calibration"
author: "Simon Jean"
date: "2023-05-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library("ggsci")
library(here)
```

# I. Demand estimation
## A. Preliminary analysis : descriptive stats

```{r load data, echo = F}
dat_p = read.csv(here("data","andrew","dat_p.csv")) #Price-quantity data (OG Paper)
dat_b = read.csv(here('data', 'andrew', "datatheif_stock.csv"))
```

First, look at the evolution of average weight per year : 
```{r avg weight, echo = F}
dat_p %>% 
  group_by(year) %>%
 summarise_at(vars(kg), list(name = mean))%>%
  ggplot(aes(x = year,  y = name))+
  geom_point()+
  theme_bw()+
  ylab('Avg weight')
```

Observe a decrease of average weight. Second, look at the evolution of price per buche through time. To do so, I compute the product of `p` and `g` (price/gram * grams of buche).

```{r pressure, echo=FALSE}
dat_p = dat_p %>%
  mutate(price_buche = g*p,
         price_kg = p*1000, 
         price_buche_kg = price_buche*1000)
dat_p %>%
  ggplot(aes(x=year))+
  geom_point(aes(y = price_buche))+
  theme_bw()
```

1. Variance of prices decreases with time
2. Average decreases

Conclusion : it seems like the market has evolved. It is hard to say whether (i) there was a crackdown a decrease in demand or (ii) supply increased. 

That goes along with what follows : the catch has increased for years we have data for : 
```{r}
dat_b %>% subset(y>2013)%>%
  ggplot(aes(x=y, y= c))+
  geom_point(size = 2)+
  theme_bw()+
  ylab("Wet catch in metric tons")+
  xlab('Year')
```
Assuming a constant demand, we can leverage that change in supply to estimate the demand function. 

### B. Data reformating
First, recover individual totoaba poached from dried buche data. To do so: 

1. `q` in `dat_p` is dried totoaba buche in tonnes : q*1000 is tonnes of dried totoaba buche
2. Given that we assume uniform distribution of totoaba size and that 1 totoaba = 500g of dried totoaba dried totoaba in kilos / 0.5 kilos -> Number of totoaba
3. Compare that to catch data :

+ In `dat_p`, take `c` catch data in metric tonnes and convert to kilos (`c*1000`)
+ Under the assumption of uniform distribution of size of caught totoaba, all weigh  25.7 kg (divide catch in kilos by average weight)
```{r, echo =F}
#JML. Added a conversion factor that transforms dry weight to wet weight (dw / 0.31 = ww)
dat_p = dat_p %>% mutate(totoaba = ((q*1000)/0.31)/.5) 
dat_b = dat_b %>% mutate(totoaba = (c*1000/25.7)) 

data.frame( totoaba_est = dat_p %>% select(totoaba) %>% unique() %>% pull(),
            totoaba_obs = dat_b %>% subset(y>2013) %>% select(totoaba)%>%pull(),
            year = c(2014, 2015, 2016, 2017))%>%
  ggplot(aes(x=year))+
  geom_line(aes(y = totoaba_est, colour= 'Recovered from dat_p'), linewidth = 1.1)+
  geom_line(aes(y = totoaba_obs, colour = 'Observed catch'), linewidth = 1.1)
  
```

There is a big difference between estimates! Maybe it makes more sense to use price data per buche and observed catch. 

### C. Attempt 1 : use price per totoaba and variation in realized catch


In what follows : 

* I use the variations in price per totoaba calculated as `price_per_totoaba = p*g` from `dat_p`. 

* I use the variations in realized catch from `dat_bc`, converted to totoaba individuals assuming uniform weight distribution (`tototaba = c*1000/25.7`)

```{r}
results = data.frame()
new_dat = merge(dat_b %>% subset(y>2013) %>% select(y,totoaba) %>%rename(year=y), dat_p %>% select(year, price_buche))
model = lm(price_buche ~ totoaba, data = new_dat)
summary(model)

demand = function(totoaba){
  y = model$coefficients[1] + model$coefficients[2]*totoaba
  return(y)
}

data.frame(x = seq(1,max(dat_b %>% subset(y>2013)%>%select(totoaba)))) %>%
  mutate(demand = demand(x))%>%
  ggplot(aes(x = x, y = demand))+
  geom_line()+
  xlab('Number of totoabas caught (unitless)')+
  ylab('Price (2019 $USD)')+
  theme_bw()

results = results %>% rbind(model$coefficients)
```

### D. Attempt 2 : Use price per totoaba and variation in estimated catch (converting dried buche tons to live totoaba)

Just to make sure we have results that are not too weird, I regress price on estimated catch. 


```{r}
new_dat = dat_p %>% select(price_buche, totoaba)
model = lm(price_buche ~ totoaba, data = new_dat)
summary(model)

demand = function(totoaba){
  y = model$coefficients[1] + model$coefficients[2]*totoaba
  return(y)
}

data.frame(x = seq(1,max(dat_b %>% subset(y>2013)%>%select(totoaba)))) %>%
  mutate(demand = demand(x))%>%
  ggplot(aes(x = x, y = demand))+
  geom_line()+
  xlab('Number of totoabas caught (unitless)')+
  ylab('Price (2019 $USD)')+
  theme_bw()+
  geom_hline(yintercept=0)

results = results %>% rbind(model$coefficients)
```

In the end, we get two demand models : 
```{r}
colnames(results) = c('Intercept (alpha)', 'beta')
print(results)
```

We keep the first model as it seem"s more pertinent. 
```{r}
results = results[1,]
```

### E. Re-estimating demand in biomass units, and with the same pooled OLS method

We want an estimate that relates prices to quantities of biomass. Without any worry of conversion, I regress prices on caught biomass measured in *metric tons*. This model assumes no lag between poaching and selling.

$$
\text{price buche}_{i} = \alpha + \beta \times catch_{i}
$$

```{r}

new_dat = merge(dat_b %>% 
                  subset(y>2013) %>% 
                  select(y,c) %>%
                  rename(year=y), 
                dat_p %>% 
                  subset(year > 2013) %>%
                  select(year, price_buche, price_kg))

new_dat = new_dat %>% mutate(c_kg = c*1000)

new_dat2 = merge(dat_b %>% 
                  subset(y>2013) %>% 
                  select(y,c) %>%
                  rename(year=y), 
                 dat_p %>% 
                   group_by(year)%>%
                   summarise_at(vars(price_kg),
                                list(avg_price_kg = mean)))
# Sample restriction to 2016
#
#new_dat2 %>% 
#  ggplot(aes(x = c,
#             y = avg_price_kg, 
#             colour = as.factor(year)))+
#  geom_point(size = 2)+
#  theme_bw

new_dat %>% 
  ggplot(aes(x = c, 
             y = price_kg, 
             colour = as.factor(year))) + 
  geom_point(size = 2)+
  theme_bw()
```

Given this summary visualization of the data:

* There seems to be two different subperiods : 2014-2015, and 2016-2017
* There are confounder between the two subperiods that may drive both a demand and a supply change. We won't get a "clean" estimate. 
* Under restrictive assumptions and to match with recent trends, we can restrict the sample to 2016-2017 to estimate demand 
* This should be a call to evaluate various demand schemes and notably to focus on other demand-sided policy interventions. 

```{r}
new_dat = new_dat %>% subset(year >2015)
model  = lm(price_kg ~ c, data = new_dat)

demand = function(biomass){
  y = model$coefficients[1] + model$coefficients[2]*biomass
  return(y)
}

data.frame(x = seq(1,max(new_dat %>%select(c)))) %>%
  mutate(demand = demand(x))%>%
  ggplot(aes(x = x, y = demand))+
  geom_line()+
  xlab('biomass of totoaba (metric tons)')+
  ylab('Price (2019 $USD)')+
  theme_bw()

summary(model)
```

# II. Cost data
## A. Poacher cost data
From this section : need to get `W`, the cost parameters of the profit functions. We assume that the measure of effort is the number of trips per year.
```{r}
df_wild = read.csv(here('data', 'w_par.csv'))
W = 8215
c = 68
results = results %>% cbind(W,c)
print(results)
```

# III. Fish parameters

Julia has set up the growth and catchability parameters
```{r}

r = 0.039
k = 20226 # in metric tons of biomass from INAPESCA
k_ = k*1000 # in kilos

catchability = 0.0005526788# in vessel trips ^-1


results = results %>% cbind(r, k_, catchability)
```

# IV. Estimating W

From Julia's calculation, we have average cost. Now the procedure is to find the $W$ parameter that minimizes the difference between a straight cost and a quadratic cost. 

```{r}
dat_w = read.csv(here("data", "w_par.csv"))
max_E = sum(dat_w$total_fleet_days_year)
```

```{r}


# Define coefficients for average costs in different estimation scenarios
avg_cost = 8215.34
min_cost = 3992.27
max_cost = 13327.92

# Define the number of trips as a continuous variable that ranges from 0 to realized trips majored by 50%
values_W = data.frame()

for (x in c(1, 1.2, 1.5)){
  
  trips = seq(0,1920*x,0.1)

# Define total costs based on different estimation scenarios
  cost_avg = avg_cost * trips
  cost_min = min_cost * trips
  cost_max = max_cost * trips

# Define trips^2
  trips_2 = trips^2

# Define quadratic cost function as a function of the coefficient W
  quadratic_cost = function(W){
    return(W*trips_2)
  }

# Approach 0 : get average cost and divide by average x
  W_avg_trip = avg_cost/(max(trips)/2)
  Ws = c(W_avg_trip = W_avg_trip)
# Approach 1: minimize sum of pointwise squared differences
  difference = function(W)(sum((cost_avg - W*trips_2)^2))


  res = optimize(difference, interval = c(0,1000))

  costs_estimation = data.frame(trips, 
                                cost_avg,
                                quad_cost_avg = quadratic_cost(W_avg_trip),
                                quad_cost_optim = quadratic_cost(res$minimum))
  Ws = append(Ws, c(W_pointwise = res$minimum))

# Second approach : minimize the sum of squared integral difference
  difference = function(W){
    y1 = W*trips_2
    return( (sum(y1) - sum(cost_avg))^2)
  }

  res = optimize(difference, interval = c(0,1000))

  Ws = append(Ws, c(W_integral = res$minimum))
  costs_estimation = costs_estimation%>%
    mutate(quad_cost_optim2 = quadratic_cost(res$minimum))
  
# Third approahc : find W such that the cost for realized trips (1920) is equal for both specifications
  W_exact = avg_cost/max_E
  Ws = append(Ws, c(W_exact_1920 = W_exact))
  Ws = append(Ws, x=x, 1)
  costs_estimation = costs_estimation%>%
    mutate(quad_cost_exact = quadratic_cost(W_exact))
  
# Fourth approache : equate marginal costs at existing equilibrium point
  # MC = 2*W*E
  # maxE = 1920
  W_MC_storage = c()
  W_MC = avg_cost/(2*max_E)
  Ws = append(Ws, c(MC_eq = W_MC))
  differ = max_E*avg_cost -W_MC*max_E^2 

  costs_estimation = costs_estimation%>%
    mutate(quad_cost_MC = quadratic_cost(W_MC)+ differ)
  values_W = rbind(values_W, Ws)

}
colnames(values_W) = names(Ws)
W_MC = c(avg_cost/(2*max_E), min_cost/(2*max_E), max_cost/(2*max_E))
# Graph : 

costs_estimation%>%
  ggplot(aes(x=trips))+
  geom_line(aes(y=cost_avg, colour = 'linear cost'), linetype = "dashed")+
  geom_line(aes(y = quad_cost_avg, colour = 'With W average of trips'))+
  geom_line(aes(y = quad_cost_optim, colour = 'Optim by pointwise difference'))+
  geom_line(aes(y = quad_cost_optim2, colour = 'Optim by integral difference'))+
  geom_line(aes(y = quad_cost_exact, colour = 'Linear = quadratic at historical equilibrium'))+
  geom_line(aes(y = quad_cost_MC, colour = 'MC equal at historical equilibrium'))+
  #geom_vline(xintercept = 1920)+
  theme_bw()+
  scale_color_aaas()
print(Ws)
```
Several points are worth noting : economic theory should favor the estimate of $W$ such that $MC(E^*)$ is equal for the linear and quadratic cost. This results in a sizeable difference, that can be fixed with a fixed cost parameter. In the end, this would yield the estimate of $W$ to be such that : 
$$
MC(E_{hist}) = 2WE_{hist} = \kappa \Rightarrow W = \frac{\kappa}{2E_{hist}}
$$
The question remains open as to if or how we control for the final difference in costs to assess profitability in equilibrium. I guess this goes to show that the discussion on the computation of profits is still not settled. 

```{r}
results = results %>% cbind(W_MC)
```

# V. Simulating the model
### A. Parameters, units of measure

```{r}
# Demand for totoaba buche : USD per unit of biomass of totoaba
alpha = model$coefficients[1] # Choke price in USD 
beta = -model$coefficients[2] # Demand coefficient for 

demand = function(totoaba){
  # Yields price per tons of totoaba
  price = alpha - beta*totoaba
  names(price) = c('price')
  return(price)
}

# Growth function for totoaba biomass (in kilograms)
growth = function(x){
  y = r*x*(1-x/k)
  return(y)
}
# conversion rate of totoaba biomass to buche biomass
conv = .5/25.7

# Catchability
sigma = 0.0005526788

# Cost parameters:
W = W_MC[1]

# gamma & v per kilogram of totoaba
dat_aqua = read.csv(here('data', 'aqua_par_farm.csv'))
dat_aqua = dat_aqua %>%
  mutate(cost_per_kilo_toto = Totoaba_Age*2,
         cost_per_ton_toto = cost_per_kilo_toto * 1000,
         cost_per_kilo_buche = cost_per_kilo_toto/conv)

gamma = dat_aqua %>% subset(Gamma>0.6 & Gamma < .7) %>% select(Gamma) %>% pull()
v = dat_aqua %>% subset(Gamma>0.6 & Gamma < .7) %>% select(cost_per_ton_toto) %>% pull()

# Cost parameter for monopoly : 
c = 2657.41 # per metric ton of totoaba
#test
c = c
```

### B. Check calibration
```{r}

qty_monop = function(x){
 y = (alpha - c)*sigma^2 * x^2 / (2*beta* sigma^2 * x^2 + 2*W)
 return(y)
}

result1 = data.frame( x = seq(1, k))%>%
  mutate(growth = growth(x),
         qty_monop = qty_monop(x),
         differ = growth - qty_monop)

result1 %>% subset(differ <1 & differ >-1)

result1 %>% ggplot(aes(x=x))+
  geom_line(aes(y = growth))+
  geom_line(aes(y = qty_monop))
#  geom_vline(xintercept =8447*1000)
```

Now, we need to think. Several things : 

1. Monopoly extraction may be viewed better as in transitory dynamics. Indeed, there is more catch than at a steady state
2. Second, demand estimates may be too small : the maximum harvest in our simulation is a little above 300 tonnes of totoaba a year. However, the recent numbers point to 400 tons.
3. It might be interesting to see, from there, what the simulation yields. It could be interesting to see if the introduction of competition creates different steady states. 

### C. Run prelim analysis : Cournot

```{r}
alpha_w = alpha
alpha_f = alpha
beta_w = beta
beta_f = beta

q_cournot_wild_own = function(x){
  y = ((sigma^2)*(x^2)*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/(4*beta_f*W + (sigma^2)*(x^2)*(4*beta_f*beta_w - (gamma^2)))
  return(y)
}
s_c_own = function(x){
  y = (2*W*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/((sigma^2)*(x^2)*(4*beta_f*beta_w - gamma^2) + 4*beta_f*W)
  return(y)
}
q_farmed_cournot = function(s){
  y = (2 * beta_w * (alpha_f - v) - gamma* (alpha_w - (s + c)) )/(4*beta_w*beta_f - gamma^2)
}

result1 = result1 %>% mutate(q_cournot_harvest = q_cournot_wild_own(x),
                             q_cournot_farmed = q_farmed_cournot(s_c_own(x)))

result1 %>%
  ggplot(aes(x = x))+
  geom_line(aes(y = growth, colour = 'Growth'))+
  geom_line(aes(y = qty_monop, colour = 'Monopoly harvest'))+
  geom_line(aes(y = q_cournot_harvest, colour = 'Cournot harvest'))+
  geom_line(aes(y = q_cournot_farmed, colour = 'Cournot farmed'))+
  theme_bw()+
  ggtitle('Equilibria for Cournot competition compared to monopoly')
```

### D. Run prelim analysis : Bertrand


```{r}
# Parameters
e   = gamma/(beta_w*beta_f - (gamma^2))
a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
b_f = beta_f/(beta_w*beta_f - (gamma^2))
b_w = beta_w/(beta_w*beta_f - (gamma^2))

s_b_own = function(x){
  y = (2*W*b_w*( b_f*(2*a_w + e*v) + c*((e^2) - 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_f*b_w - (e^2)) + 2*W*b_w*(2*b_w*b_f - (e^2)))
  return(y)
}

q_b_own = function(x){
  y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
  return(y)
}

quantity_farmed = function(s){
  y = b_f *(2*b_w*a_f + v*(e^2 - 2*b_w*b_f) + e*(a_w + (s+c)*b_w))/(4*b_f*b_w - e^2)
  return(y)
}

result1 = result1 %>% mutate(q_bertrand_harvest = q_b_own(x),
                             q_bertrand_farmed = quantity_farmed(s_b_own(x)))

result1 %>%
  ggplot(aes(x = x))+
  geom_line(aes(y = qty_monop, colour = 'Monopoly harvest'))+
  geom_line(aes(y = growth, colour = 'Growth'))+
  geom_line(aes(y = q_bertrand_harvest, colour = 'Betrand harvest'))+
  geom_line(aes(y = q_bertrand_farmed, colour = 'Bertrand farmed'))+
  theme_bw()
```

Conclusion from preliminary results : 
 
1. Competition only will not change the demise of totoaba
2. It may help to reach slightly larger steady state values, but will eventually lead to a drastic depletion of the stock
3. In order to change that dynamic, several interventions would be needed : 
* For example, one could think about different $(\gamma, v)$ pairs
* Or consider the effect of being more competitive at the farming level

4. It is unclear what we can do to go beyond our results with this model. 

# Analysis of new scenarios?

For example, can we think of ways that would curb the exploitation? For example, what about cracking down on demand, or technological research that makes production less costly? Or compare the impact of different cost measures for poaching, at the trader and poacher level? 



