---
title: "Parameters estimation for calibration"
author: "Simon Jean"
date: "2023-05-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library("ggsci")
library(here)
```

# I. Demand estimation
## A. Preliminary analysis : descriptive stats

```{r load data, echo = F}
dat_p = read.csv(here("data","andrew","dat_p.csv")) #Price-quantity data (OG Paper)
dat_b = read.csv(here('data', 'andrew', "datatheif_stock.csv"))
```

First, look at the evolution of average weight per year : 
```{r avg weight, echo = F}
dat_p %>% 
  group_by(year) %>%
 summarise_at(vars(kg), list(name = mean))%>%
  ggplot(aes(x = year,  y = name))+
  geom_point()+
  theme_bw()+
  ylab('Avg weight')
```

Observe a decrease of average weight. Second, look at the evolution of price per buche through time. To do so, I compute the product of `p` and `g` (price/gram * grams of buche).

```{r pressure, echo=FALSE}
dat_p = dat_p %>%
  mutate(price_buche = g*p,
         price_kg = p*1000, 
         price_buche_kg = price_buche*1000)
dat_p %>%
  ggplot(aes(x=year))+
  geom_point(aes(y = price_buche))+
  theme_bw()
```

1. Variance of prices decreases with time
2. Average decreases

Conclusion : it seems like the market has evolved. It is hard to say whether (i) there was a crackdown a decrease in demand or (ii) supply increased. 

That goes along with what follows : the catch has increased for years we have data for : 
```{r}
dat_b %>% subset(y>2013)%>%
  ggplot(aes(x=y, y= c))+
  geom_point(size = 2)+
  theme_bw()+
  ylab("Wet catch in metric tons")+
  xlab('Year')
```
Assuming a constant demand, we can leverage that change in supply to estimate the demand function. 

### B. Data reformating
First, recover individual totoaba poached from dried buche data. To do so: 

1. `q` in `dat_p` is dried totoaba buche in tonnes : q*1000 is tonnes of dried totoaba buche
2. Given that we assume uniform distribution of totoaba size and that 1 totoaba = 500g of dried totoaba dried totoaba in kilos / 0.5 kilos -> Number of totoaba
3. Compare that to catch data :

+ In `dat_p`, take `c` catch data in metric tonnes and convert to kilos (`c*1000`)
+ Under the assumption of uniform distribution of size of caught totoaba, all weigh  25.7 kg (divide catch in kilos by average weight)
```{r, echo =F}
#JML. Added a conversion factor that transforms dry weight to wet weight (dw / 0.31 = ww)
dat_p = dat_p %>% mutate(totoaba = ((q*1000)/0.31)/.5) 
dat_b = dat_b %>% mutate(totoaba = (c*1000/25.7)) 

data.frame( totoaba_est = dat_p %>% select(totoaba) %>% unique() %>% pull(),
            totoaba_obs = dat_b %>% subset(y>2013) %>% select(totoaba)%>%pull(),
            year = c(2014, 2015, 2016, 2017))%>%
  ggplot(aes(x=year))+
  geom_line(aes(y = totoaba_est, colour= 'Recovered from dat_p'), linewidth = 1.1)+
  geom_line(aes(y = totoaba_obs, colour = 'Observed catch'), linewidth = 1.1)
  
```

There is a big difference between estimates! Maybe it makes more sense to use price data per buche and observed catch. 

### C. Attempt 1 : use price per totoaba and variation in realized catch


In what follows : 

* I use the variations in price per totoaba calculated as `price_per_totoaba = p*g` from `dat_p`. 

* I use the variations in realized catch from `dat_bc`, converted to totoaba individuals assuming uniform weight distribution (`tototaba = c*1000/25.7`)

```{r}
results = data.frame()
new_dat = merge(dat_b %>% subset(y>2013) %>% select(y,totoaba) %>%rename(year=y), dat_p %>% select(year, price_buche))
model = lm(price_buche ~ totoaba, data = new_dat)
summary(model)

demand = function(totoaba){
  y = model$coefficients[1] + model$coefficients[2]*totoaba
  return(y)
}

data.frame(x = seq(1,max(dat_b %>% subset(y>2013)%>%select(totoaba)))) %>%
  mutate(demand = demand(x))%>%
  ggplot(aes(x = x, y = demand))+
  geom_line()+
  xlab('Number of totoabas caught (unitless)')+
  ylab('Price (2019 $USD)')+
  theme_bw()

results = results %>% rbind(model$coefficients)
```

### D. Attempt 2 : Use price per totoaba and variation in estimated catch (converting dried buche tons to live totoaba)

Just to make sure we have results that are not too weird, I regress price on estimated catch. 


```{r}
new_dat = dat_p %>% select(price_buche, totoaba)
model = lm(price_buche ~ totoaba, data = new_dat)
summary(model)

demand = function(totoaba){
  y = model$coefficients[1] + model$coefficients[2]*totoaba
  return(y)
}

data.frame(x = seq(1,max(dat_b %>% subset(y>2013)%>%select(totoaba)))) %>%
  mutate(demand = demand(x))%>%
  ggplot(aes(x = x, y = demand))+
  geom_line()+
  xlab('Number of totoabas caught (unitless)')+
  ylab('Price (2019 $USD)')+
  theme_bw()+
  geom_hline(yintercept=0)

results = results %>% rbind(model$coefficients)
```

In the end, we get two demand models : 
```{r}
colnames(results) = c('Intercept (alpha)', 'beta')
print(results)
```

We keep the first model as it seem"s more pertinent. 
```{r}
results = results[1,]
```

### E. Re-estimating demand in biomass units, and with the same pooled OLS method

We want an estimate that relates prices to quantities of biomass. However, biomass does not refer to the quantity of product here. It relates to the quantity of fish, which produce buche. Therefore, we need a conversion rate. Using data from INAPESCA, we use the following : 
$$
1\text{ kilo of biomass} \equiv \frac{0.5 \text{ kg of buche}}{25.7 \text{kg}} \approx 0.019
$$
```{r}
conv = .5/25.7
```

From there, I regress prices on the biomass, using the conversion rate : 
$$
\text{price buche}_{i} = \alpha + \beta\times conv \times catch_{i}
$$

After all, I'm not sure this is interesting. We want to have price per unit of biomass, and express everything per unit of biomass, no? 

```{r}
new_dat = merge(dat_b %>% 
                  subset(y>2013) %>% 
                  select(y,c) %>%
                  rename(year=y), 
                dat_p %>% 
                  select(year, price_buche, price_kg))

new_dat = new_dat %>% mutate(c_kg = c*1000,
                             c_buche_kg = c_kg * conv,
                             c_buche = c * conv)

model  = lm(price_kg ~ c_kg, data = new_dat)
model2 = lm(price_kg ~ c_buche_kg, data = new_dat)

demand = function(biomass){
  y = model$coefficients[1] + model$coefficients[2]*biomass
  return(y)
}

data.frame(x = seq(1,max(new_dat %>%select(c))*1000, 10)) %>%
  mutate(demand = demand(x))%>%
  ggplot(aes(x = x, y = demand))+
  geom_line()+
  xlab('biomass of totoaba (kg)')+
  ylab('Price (2019 $USD)')+
  theme_bw()

summary(model)
```

# II. Cost data
## A. Poacher cost data
From this section : need to get `W`, the cost parameters of the profit functions. We assume that the measure of effort is the number of trips per year.
```{r}
df_wild = read.csv(here('data', 'w_par.csv'))
W = 8215
c = 68
results = results %>% cbind(W,c)
print(results)
```

## B. Farming cost

```{r}
df_farm = read.csv(here("data", "aqua_par_farm.csv"))
df_farm = df_farm %>%
  mutate(cost_per_toto = Cost_feed_kgyear/Number_Individuals)
df_farm %>% ggplot(aes(x=Totoaba_Age))+
  geom_point(aes(y=cost_per_toto, colour = 'Cost'))

```

# III. Fish parameters

Julia has set up the growth and catchability parameters
```{r}

r = 0.039
k = 20226 # in metric tons of biomass from INAPESCA
k_ = k*1000 # in kilos

catchability = 0.0005526788# in vessel trips ^-1


results = results %>% cbind(r, k_, catchability)
```

# IV. Estimating W

From Julia's calculation, we have average cost. Now the procedure is to find the $W$ parameter that minimizes the difference between a straight cost and a quadratic cost. 

```{r}
dat_w = read.csv(here("data", "w_par.csv"))
max_E = sum(dat_w$total_fleet_days_year)
```

```{r}


# Define coefficients for average costs in different estimation scenarios
avg_cost = 8215.34
min_cost = 3992.27
max_cost = 13327.92

# Define the number of trips as a continuous variable that ranges from 0 to realized trips majored by 50%
values_W = data.frame()

for (x in c(1, 1.2, 1.5)){
  
  trips = seq(0,1920*x,0.1)

# Define total costs based on different estimation scenarios
  cost_avg = avg_cost * trips
  cost_min = min_cost * trips
  cost_max = max_cost * trips

# Define trips^2
  trips_2 = trips^2

# Define quadratic cost function as a function of the coefficient W
  quadratic_cost = function(W){
    return(W*trips_2)
  }

# Approach 0 : get average cost and divide by average x
  W_avg_trip = avg_cost/(max(trips)/2)
  Ws = c(W_avg_trip = W_avg_trip)
# Approach 1: minimize sum of pointwise squared differences
  difference = function(W)(sum((cost_avg - W*trips_2)^2))


  res = optimize(difference, interval = c(0,1000))

  costs_estimation = data.frame(trips, 
                                cost_avg,
                                quad_cost_avg = quadratic_cost(W_avg_trip),
                                quad_cost_optim = quadratic_cost(res$minimum))
  Ws = append(Ws, c(W_pointwise = res$minimum))

# Second approach : minimize the sum of squared integral difference
  difference = function(W){
    y1 = W*trips_2
    return( (sum(y1) - sum(cost_avg))^2)
  }

  res = optimize(difference, interval = c(0,1000))

  Ws = append(Ws, c(W_integral = res$minimum))
  costs_estimation = costs_estimation%>%
    mutate(quad_cost_optim2 = quadratic_cost(res$minimum))
  
# Third approahc : find W such that the cost for realized trips (1920) is equal for both specifications
  W_exact = avg_cost/max_E
  Ws = append(Ws, c(W_exact_1920 = W_exact))
  Ws = append(Ws, x=x, 1)
  costs_estimation = costs_estimation%>%
    mutate(quad_cost_exact = quadratic_cost(W_exact))
  
# Fourth approache : equate marginal costs at existing equilibrium point
  # MC = 2*W*E
  # maxE = 1920
  W_MC_storage = c()
  W_MC = avg_cost/(2*max_E)
  Ws = append(Ws, c(MC_eq = W_MC))
  differ = max_E*avg_cost -W_MC*max_E^2 

  costs_estimation = costs_estimation%>%
    mutate(quad_cost_MC = quadratic_cost(W_MC)+ differ)
  values_W = rbind(values_W, Ws)

}
colnames(values_W) = names(Ws)
W_MC = c(avg_cost/(2*max_E), min_cost/(2*max_E), max_cost/(2*max_E))
# Graph : 

costs_estimation%>%
  ggplot(aes(x=trips))+
  geom_line(aes(y=cost_avg, colour = 'linear cost'), linetype = "dashed")+
  geom_line(aes(y = quad_cost_avg, colour = 'With W average of trips'))+
  geom_line(aes(y = quad_cost_optim, colour = 'Optim by pointwise difference'))+
  geom_line(aes(y = quad_cost_optim2, colour = 'Optim by integral difference'))+
  geom_line(aes(y = quad_cost_exact, colour = 'Linear = quadratic at historical equilibrium'))+
  geom_line(aes(y = quad_cost_MC, colour = 'MC equal at historical equilibrium'))+
  #geom_vline(xintercept = 1920)+
  theme_bw()+
  scale_color_aaas()
print(Ws)
```
Several points are worth noting : economic theory should favor the estimate of $W$ such that $MC(E^*)$ is equal for the linear and quadratic cost. This results in a sizeable difference, that can be fixed with a fixed cost parameter. In the end, this would yield the estimate of $W$ to be such that : 
$$
MC(E_{hist}) = 2WE_{hist} = \kappa \Rightarrow W = \frac{\kappa}{2E_{hist}}
$$
The question remains open as to if or how we control for the final difference in costs to assess profitability in equilibrium. I guess this goes to show that the discussion on the computation of profits is still not settled. 

```{r}
results = results %>% cbind(W_MC)
```

# V. Simulating the model
### A. Parameters, units of measure

```{r}
# Demand for totoaba buche : USD per unit of biomass of totoaba
alpha = model$coefficients[1] # Choke price in USD 
beta = -model$coefficients[2] # Demand coefficient for 

demand = function(buche){
  # Yields price per kilogram of totoaba
  price = alpha - beta*buche
  names(price) = c('price')
  return(price)
}

# Growth function for totoaba biomass (in kilograms)
growth = function(x){
  y = r*x*(1-x/k_)
  return(y)
}
# conversion rate of totoaba biomass to buche biomass
conv = .5/25.7

# Catchability
sigma = 0.0005526788

# Cost parameters:
W = W_MC[1]

# gamma & v per kilogram of totoaba
dat_aqua = read.csv(here('data', 'aqua_par_farm.csv'))
dat_aqua = dat_aqua %>%
  mutate(cost_per_kilo_toto = Totoaba_Age*2,
         cost_per_kilo_buche = cost_per_kilo_toto/conv)

gamma = dat_aqua %>% subset(Gamma>0.6 & Gamma < .65) %>% select(Gamma) %>% pull()
v = dat_aqua %>% subset(Gamma>0.6 & Gamma < .65) %>% select(cost_per_kilo_toto) %>% pull()

# Cost parameter for monopoly : 
c = 2657.41 # per metric ton of totoaba
c = c/1000
```

### B. Check calibration
```{r}
qty_monop = function(x){
 y = (alpha - c)*sigma^2 * x^2 / (2*beta* sigma^2 * x^2 + 2*W)
 return(y)
}

result1 = data.frame( x = seq(1, k_, 10))%>%
  mutate(growth = growth(x),
         qty_monop = qty_monop(x),
         differ = growth - qty_monop)

result1 %>% subset(differ <1 & differ >-1)

#result1 %>% ggplot(aes(x=x))+
#  geom_line(aes(y = growth))+
#  geom_line(aes(y = qty_monop))+
#  geom_vline(xintercept =8447*1000)

result1 %>% ggplot(aes(x = x, y = growth)) +geom_line()
result1 %>% ggplot(aes(x = x, y = qty_monop)) +geom_line()
```





