---
title: "Sensitivity analysis"
author: "Simon Jean"
date: "2023-05-17"
output: html_document
---

# Sensitivity analysis

```{r setup, include = F}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library("ggsci")
library(here)
library(knitr)
library(stargazer)
library(parallel)

rm(list = ls())
```


## A. Load parameters for baseline

```{r}

calibration = read.csv(here('data', 'calibration_params.csv'))

for(i in 1:nrow(calibration)){
  assign(calibration$params[i], calibration$value[i])
}
```

## B. Define the parameters for sensitivity analysis

For this version of the sensitivity analysis, I generate combinations based only on 1 variable being different. This may make more sense. The sensitivity analysis is ran for cost and demand data. Other variables can be included, and other values can be included. 

```{r}
# Sensitivity analysis around v, gamma, alpha, W, c

# I. Get a baseline dataframe with all the parameters we may want to test. ####

# It is a dataframe because it includes a lot of possible values for v and gamma

baseline = data.frame(beta = beta, 
                      alpha = alpha, 
                      gamma = gamma, 
                      W = W_mid, 
                      c = c,
                      v = v,
                      r = r, 
                      k = k,
                      sigma = sigma,
                      spec = 'baseline', 
                      transformation = NA)

params_sensitivity = baseline

# II. Define all the parameter values we want to test: ####
# Important : define those values as COEFFICIENTS to be applied to the variables
# Little sloppy, but the idea is to make sure all vectors are the same length
# for storage in dataframe
v_sens = c(.01, 0.05, .1, .5, .6, .7, .8, 1.2)
gamma_sens = c(0.0001, .01, .1/gamma, .2/gamma, .5/gamma, .8/gamma, .95/gamma, .9999/gamma)
c_sens = c(5,  10, 20,30, 40, 45, 50, NA)
alpha_sens = c(.5, .6, .8, 1.2, 1.5, 1.6, NA, NA)
W_sens = c(W_low/W_mid,W_high/W_mid, 2, 4, 6, NA, NA, NA)
beta_sens = c(.5, .8, 1.2, 1.5, NA, NA, NA, NA)
# Store into data.frame
sensitivity_values = data.frame()%>%
  rbind(v_sens, gamma_sens, c_sens, alpha_sens, W_sens, beta_sens)
sensitivity_values = cbind(data.frame(c('v', 'gamma', 'c', 'alpha', 'W', 'beta')),
                           sensitivity_values)

colnames(sensitivity_values) = append(c('var'), c(paste0('val',1:length(W_sens))))

# III. Loop to get the data we want ####
# Here, loop over names.
for(name in sensitivity_values$var){
  dat = baseline
  to_mult = sensitivity_values %>% subset(var==name) %>% select(-var)%>% unlist()
  # Take all the values that are non NA we want to transform baseline data with
  to_mult = to_mult[!is.na(to_mult)]

  # Loop over each value : store data with (i) what variable is modified and
  # (ii) the values we apply to them
  for (val in to_mult){
    dat = baseline
  
    idea= as.name(name)
    dat[[idea]] = dat%>%
      select(all_of(idea))%>%
      unlist()*val
    dat$spec = paste(name)
    dat$transformation = val
    params_sensitivity = rbind(params_sensitivity, dat)
  }
}
a = expand_grid(c_sens, v_sens)
colnames(a) = c('c', 'v')
a = cbind(baseline %>% select(-c('c', 'v', 'spec', 'transformation'))%>% slice(rep(1:n(), each = nrow(a))), a)
a = a %>% mutate(spec = 'c and v', 
                 transformation = paste(c,' and ', v))

params_sensitivity = rbind(params_sensitivity, a)
rm(a)
print(paste0('There are ', nrow(params_sensitivity)," combinations to test" ))
```


## C. Define function to run model

In this section, I have not yet perfected the outputs of the models. I think it might be good to keep it like that, and then to define a second function to track the equilibrium outputs. So far, the functions return the equilibrium values of the stock. A second module (maybe tomorrow) will compute : 

* Equilibrium farmed and harvested quantities
* Prices paid to poachers
* Profits


```{r}
run_model = function(){
  # Function to run the model simulation
  # 0. Define growth = 
  growth = function(x){
    y = r*x*(1-x/k)
    return(y)
  }
  
  # 1. Run monopoly
  qty_monop = function(x){
    y = (alpha - c)*sigma^2 * x^2 / (2*beta* sigma^2 * x^2 + 2*W)
    return(y)
  }
  # Store results
  result1 = data.frame( x = seq(1, k))%>%
    mutate(growth = growth(x),
           qty_monop = qty_monop(x),
           differ = growth - qty_monop)
  # 2. Run Cournot
  alpha_w = alpha
  alpha_f = alpha
  beta_w = beta
  beta_f = beta

  q_cournot_wild_own = function(x){
    y = ((sigma^2)*(x^2)*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/(4*beta_f*W +     (sigma^2)*(x^2)*(4*beta_f*beta_w - (gamma^2)))
    return(y)
  }
  result1 = result1 %>% mutate(q_cournot_harvest = q_cournot_wild_own(x))
  
  # Run Betrand : 
  e   = gamma/(beta_w*beta_f - (gamma^2))
  a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
  a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
  b_f = beta_f/(beta_w*beta_f - (gamma^2))
  b_w = beta_w/(beta_w*beta_f - (gamma^2))
  
  q_b_own = function(x){
    y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
    return(y)
  }
  

  
  result1 = result1 %>% mutate(q_bertrand_harvest = q_b_own(x))
  
  # Find steady states : 
  
  result1 = result1 %>% mutate(ss_monop = growth - qty_monop,
                               ss_cournot = growth - q_cournot_harvest,
                               ss_bertrand = growth - q_bertrand_harvest)
  steady_states = c()
  harvests = c()
  for(variable in c('ss_monop', 'ss_cournot', 'ss_bertrand')){
    # Comment that
    ss = which(sign(eval(parse(text = paste0('result1$',variable)))) != lag(sign(eval(parse(text = paste0('result1$', variable))))))
    
    if(length(ss)==1){
      steady_states = append(steady_states, c(result1[ss, 1], 
                                              NA,
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    NA, 
                                    NA))
    }
    else if(length(ss)==2){
      steady_states = append(steady_states, c(result1[ss[1], 1], 
                                              result1[ss[2], 1],
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    NA))
    }
    else if(length(ss)==3){
      steady_states = append(steady_states, c(result1[ss[1],1], 
                                              result1[ss[2],1],
                                              result1[ss[3],1]))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    growth(ss[3])))
    }
    else if(length(ss)==0){
      steady_states = append(steady_states, c(NA, NA, NA))
      harvests = append(harvests, c(NA, NA, NA))
    }
    
  }
  # Results : 
  results = append(append(params,
                   steady_states),
                   harvests)
  
  return(results)
}

#Define parallelized version
run_model_par = function(params){
  
  k     = params[1]
  sigma = params[2]
  W     = params[3]
  beta  = params[4]
  v     = params[6]
  c     = params[7]
  alpha = params[8]
  r     = params[9]
  gamma = params[10]

  # Function to run the model simulation
  # 0. Define growth = 
  growth = function(x){
    y = r*x*(1-x/k)
    return(y)
  }
  
  # 1. Run monopoly
  qty_monop = function(x){
    y = (alpha - c)*sigma^2 * x^2 / (2*beta* sigma^2 * x^2 + 2*W)
    return(y)
  }
  # Store results
  result1 = data.frame(x = seq(1, k))%>%
    mutate(growth = growth(x),
           qty_monop = qty_monop(x),
           differ = growth - qty_monop)
  # 2. Run Cournot
  alpha_w = alpha
  alpha_f = alpha
  beta_w = beta
  beta_f = beta

  q_cournot_wild_own = function(x){
    y = ((sigma^2)*(x^2)*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/(4*beta_f*W +     (sigma^2)*(x^2)*(4*beta_f*beta_w - (gamma^2)))
    return(y)
  }
  
  s_c_own = function(x){
    y = (2*W*(2*beta_f*(alpha_w - c) - gamma*(alpha_f - v)))/((sigma^2)*(x^2)*(4*beta_f*beta_w - gamma^2) + 4*beta_f*W)
    return(y)
  }
  q_farmed_cournot = function(s){
    y = (2 * beta_w * (alpha_f - v) - gamma* (alpha_w - (s + c)) )/(4*beta_w*beta_f - gamma^2)
    return(y)
  }
  
  result1 = result1 %>% mutate(q_cournot_harvest = q_cournot_wild_own(x),
                               q_cournot_farmed = q_farmed_cournot(s_c_own(x)))
  
  # Run Betrand : 
  e   = gamma/(beta_w*beta_f - (gamma^2))
  a_f = (alpha_f*beta_w - alpha_w*gamma)/(beta_w*beta_f - (gamma^2))
  a_w = (alpha_w*beta_f - alpha_f*gamma)/(beta_w*beta_f - (gamma^2))
  b_f = beta_f/(beta_w*beta_f - (gamma^2))
  b_w = beta_w/(beta_w*beta_f - (gamma^2))
  
  s_b_own = function(x){
    y = (2*W*b_w*( b_f*(2*a_w + e*v) + c*((e^2) - 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_f*b_w - (e^2)) + 2*W*b_w*(2*b_w*b_f - (e^2)))
    return(y)
  }
  
  q_b_own = function(x){
    y = ((sigma^2)*(x^2)*b_w*(b_f*(2*a_w+e*v) + c*((e^2)- 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_w*b_f - (e^2)) + 2*W*b_w*(2*b_f*b_w - (e^2)))
    return(y)
  }
  
  quantity_farmed = function(s){
    y = b_f *(2*b_w*a_f + v*(e^2 - 2*b_w*b_f) + e*(a_w + (s+c)*b_w))/(4*b_f*b_w - e^2)
    return(y)
  }
  
  result1 = result1 %>% mutate(q_bertrand_harvest = q_b_own(x),
                               q_bertrand_farmed = quantity_farmed(s_b_own(x)))
  
  # Find steady states : 
  result1 = result1 %>% mutate(ss_monop = growth - qty_monop,
                               ss_cournot = growth - q_cournot_harvest,
                               ss_bertrand = growth - q_bertrand_harvest)
  steady_states = c()
  harvests = c()
  for(variable in c('ss_monop', 'ss_cournot', 'ss_bertrand')){
    # Comment that
    ss = which(sign(eval(parse(text = paste0('result1$',variable)))) != lag(sign(eval(parse(text = paste0('result1$', variable))))))
    
    if(length(ss)==1){
      steady_states = append(steady_states, c(result1[ss, 1], 
                                              NA,
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    NA, 
                                    NA))
    }else if(length(ss)==2){
      steady_states = append(steady_states, c(result1[ss[1], 1], 
                                              result1[ss[2], 1],
                                              NA))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    NA))
    }else if(length(ss)==3){
      steady_states = append(steady_states, c(result1[ss[1],1], 
                                              result1[ss[2],1],
                                              result1[ss[3],1]))
      harvests = append(harvests, c(growth(ss[1]), 
                                    growth(ss[2]), 
                                    growth(ss[3])))
    }else if(length(ss)==0){
      steady_states = append(steady_states, c(NA, NA, NA))
      harvests = append(harvests, c(NA, NA, NA))
    }
    
  }
  
  # Find harvests : 

  # Compute prices : 
  
  # Compute profits :
  
  
  return(append(params,steady_states, harvests))
}
```


## D. Run

Two ways : 

* If `params_sensitivity` is not too large (less than 10,000 rows), can run it on the computer, it's easy

* If too long, use multiprocessing to perform analysis. I define chunks and then let the code run on the chunks of data. To run the model, define `r run_ = T`, otherwise leave it as is, and load the data. `

To deal with data, there are two layers : 

* Column `spec` displays which variable has been tweaked. For example, if one wants to analyze data for changed values of `v`, run `store %>% subset(spec == 'v')`, or when $c$ and $v$ move at the same time, `store %>% subset(spec == 'c and v')`.

* Second, column `transformation` can be used to color the graphs. If you want to check what how different values of `v` may impact the results, you can subset based on `transformation`. To find where each was applied, check section B's code

```{r}
run_ = T

if(exists(here('data','sensitivity_steady_states.csv'))){
  run = F
}

if(run_==T){
  # No need for parallel computing with small dataset
  if(nrow(params_sensitivity)<10000){
    
    to_assign = colnames(params_sensitivity)
    to_assign = to_assign[1:9]
    store = data.frame()
    
    # Loop over all rows
    for(row in 1:nrow(params_sensitivity)){
      
      # First, assign environment variable
      for(variable in to_assign){
        assign(variable, 
               params_sensitivity[row,] %>% 
                 select(all_of(variable)) %>% 
                 pull())
      }
      # Then store data : 
      params = params_sensitivity[row,]%>%
        unlist()
      
      store = rbind(store, 
                    run_model())
    }
    # Get names
    colnames(store) = append(colnames(params_sensitivity), 
                             c('ss_monop1', "ss_monop2", "ss_monop3", 'ss_cournot1',
                               'ss_cournot2', 'ss_cournot3', 'ss_bertrand1', "ss_bertrand2", 
                               'ss_bertrand3', 'harvest_monop1', 'harvest_monop2',
                               'harvest_monop3', 'harvest_cournot1','harvest_cournot2',
                               'harvest_cournot3', 'harvest_bertrand1', 'harvest_bertrand2',
                               'harvest_bertrand3'))
    store['spec'] = as.factor(store$spec)
    store['transformation'] = as.factor(store$transformation)
    store = store %>% mutate_if(is.character, as.numeric)
    # Now that all the steady states stock and harvest rates are computed, do a big mutate for other output variables
    # i. Define output functions : 
    ### Monopoly
    price_monop          = function(h, alpha, beta){
      y = alpha - beta*h
      return(y)
    }
    price_poachers_monop = function(x, alpha, beta, sigma, c, W){
      y = (alpha - c)*W/(beta*sigma^2*x^2 + W)
      return(y)
    }
    profit_monop         = function(h,x,alpha, beta, sigma, c, W){
      y = price_monop(h, alpha, beta)*h - (c + price_poachers_monop(x, alpha, beta, sigma, c, W))*h
      return(y)
    }
    # test
    store = store %>% mutate(price_monop1          = price_monop(harvest_monop1, alpha, beta),
                             price_monop2          = price_monop(harvest_monop2, alpha, beta),
                             price_monop3          = price_monop(harvest_monop3, alpha, beta),
                             price_poachers_monop1 = price_poachers_monop(ss_monop1, alpha, beta, sigma, c, W),
                             price_poachers_monop2 = price_poachers_monop(ss_monop2, alpha, beta, sigma, c, W),
                             price_poachers_monop3 = price_poachers_monop(ss_monop3, alpha, beta, sigma, c, W),
                             profit_monop1         = profit_monop(harvest_monop1,ss_monop1,alpha, beta, sigma, c, W),
                             profit_monop2         = profit_monop(harvest_monop2,ss_monop2,alpha, beta, sigma, c, W),
                             profit_monop3         = profit_monop(harvest_monop3,ss_monop3,alpha, beta, sigma, c, W))
    ### Cournot 
    s_c_own          = function(x, alpha, beta, gamma, sigma, c, W ){
      y = (2*W*(2*beta*(alpha - c) - gamma*(alpha - v)))/((sigma^2)*(x^2)*(4*beta*beta - gamma^2) + 4*beta*W)
      return(y)
    }
    q_farmed_cournot = function(s, alpha, beta, gamma, c, v){
      y = (2 * beta * (alpha - v) - gamma* (alpha - (s + c)) )/(4*beta*beta - gamma^2)
      return(y)
    }
    profit_farm      = function(hf, hw, alpha, beta, gamma, v){
      y = (alpha - beta*hf - gamma*hw - v)*hf
      return(y)
    }
    profit_trader    = function(hf, hw, x, alpha, beta, gamma, c, W){
      y = (alpha - beta*hw - gamma*hf - s_c_own(x, alpha, beta, gamma, sigma, c, W) - c)*hw
      return(y)
    }
    price_farmed     = function(alpha, beta, gamma, hw, hf){
      y = alpha - beta*hf - gamma*hf
      return(y)
    }
    price_wild       = function(alpha, beta, gamma, hw, hf){
      y = alpha - beta*hw - gamma*hf
      return(y)
    }
    
    store = store %>% mutate(price_poachers_cournot1 = s_c_own(ss_cournot1, alpha, beta, gamma, sigma, c, W),
                             farmed_cournot1         = q_farmed_cournot(price_poachers_cournot1,alpha, beta, gamma, c, v),
                             p_farmed_cournot1       = price_farmed(alpha, beta, gamma, harvest_cournot1, farmed_cournot1),
                             p_wild_cournot1         = price_wild(alpha, beta, gamma, harvest_cournot1, farmed_cournot1),
                             profit_farmed_cournot1  = profit_farm(farmed_cournot1, harvest_cournot1, alpha, beta, gamma, v),
                             profit_trader_cournot1  = profit_trader(farmed_cournot1, harvest_cournot1, ss_cournot1, alpha, beta, gamma, c,W),
                            # Second steady state                        
                             price_poachers_cournot2 = s_c_own(ss_cournot2, alpha, beta, gamma, sigma, c, W),
                             farmed_cournot2         = q_farmed_cournot(price_poachers_cournot2,alpha, beta, gamma, c, v),
                             p_farmed_cournot2       = price_farmed(alpha, beta, gamma, harvest_cournot2, farmed_cournot2),
                             p_wild_cournot2         = price_wild(alpha, beta, gamma, harvest_cournot2, farmed_cournot2),
                             profit_farmed_cournot2  = profit_farm(farmed_cournot2, harvest_cournot2, alpha, beta, gamma, v),
                             profit_trader_cournot2  = profit_trader(farmed_cournot2, harvest_cournot2, ss_cournot2, alpha, beta, gamma, c,W),
                            # Third steady state                        
                             price_poachers_cournot3 = s_c_own(ss_cournot3, alpha, beta, gamma, sigma, c, W),
                             farmed_cournot3         = q_farmed_cournot(price_poachers_cournot3,alpha, beta, gamma, c, v),
                             p_farmed_cournot3       = price_farmed(alpha, beta, gamma, harvest_cournot3, farmed_cournot3),
                             p_wild_cournot3         = price_wild(alpha, beta, gamma, harvest_cournot3, farmed_cournot3),
                             profit_farmed_cournot3  = profit_farm(farmed_cournot3, harvest_cournot3, alpha, beta, gamma, v),
                             profit_trader_cournot3  = profit_trader(farmed_cournot3, harvest_cournot3, ss_cournot3, alpha, beta, gamma, c,W))
    # Bertrand
    store = store %>% mutate(e   = gamma/(beta*beta - (gamma^2)),
                             a_f = (alpha*beta - alpha*gamma)/(beta*beta - (gamma^2)),
                             a_w = (alpha*beta - alpha*gamma)/(beta*beta - (gamma^2)),
                             b_f = beta/(beta*beta - (gamma^2)),
                             b_w = beta/(beta*beta - (gamma^2)))
  
  s_b_own          = function(x, a_f, a_w, b_f, b_w, e, W, c){
    y = (2*W*b_w*( b_f*(2*a_w + e*v) + c*((e^2) - 2*b_f*b_w) + e*a_f))/((sigma^2)*(x^2)*(4*b_f*b_w - (e^2)) + 2*W*b_w*(2*b_w*b_f - (e^2)))
    return(y)
  }
  quantity_farmed  = function(s, a_f, a_w, b_f, b_w, e, W, c){
    y = b_f *(2*b_w*a_f + v*(e^2 - 2*b_w*b_f) + e*(a_w + (s+c)*b_w))/(4*b_f*b_w - e^2)
    return(y)
  }
  price_farmed     = function(s, a_f, a_w, b_f, b_w, e, c){
    y = (2*b_w*(a_f + v*b_f) + e*(a_w + b_w*(s+c)))/(4*b_f*b_w - e^2)
    return(y)
  }
  price_trader     = function(s, a_f, a_w, b_f, b_w, e, c){
    y = (2*b_f *(a_w+b_w*(s+c))+e*(a_f +v*b_f))/(4*b_f*b_w - e^2)
    return(y)
  }
  profit_farm      = function(pw, pf, a_f, b_f, e, v){
    y = (pf - v)*(a_f - b_f*pf + e*pw)
    return(y)
  }
  profit_trader    = function(pw, pf, a_w, b_w, e, s, c){
    y = (pw - s - c)*(a_w - b_w*pw + e*pf)
    return(y)
  }
    
  store = store %>% mutate(price_poachers_bertrand1 = s_b_own(ss_bertrand1, a_f, a_w, b_f, b_w, e, W, c),
                           farmed_bertrand1         = quantity_farmed(price_poachers_bertrand1, a_f, a_w, b_f, b_w, e, W, c),
                           p_farmed_bertrand1       = price_farmed(price_poachers_bertrand1, a_f, a_w, b_f, b_w, e, c),
                           p_wild_bertrand1         = price_trader(price_poachers_bertrand1, a_f, a_w, b_f, b_w, e, c),
                           profit_farmed_bertrand1  = profit_farm(p_wild_bertrand1, p_farmed_bertrand1, a_f, b_f, e, v),
                           profit_trader_bertrand1  = profit_trader(p_wild_bertrand1, p_farmed_bertrand1, a_w, b_w, e, price_poachers_bertrand1, c),
                           # Second steady state:
                           price_poachers_bertrand2 = s_b_own(ss_bertrand2, a_f, a_w, b_f, b_w, e, W, c),
                           farmed_bertrand2         = quantity_farmed(price_poachers_bertrand2, a_f, a_w, b_f, b_w, e, W, c),
                           p_farmed_bertrand2       = price_farmed(price_poachers_bertrand2, a_f, a_w, b_f, b_w, e, c),
                           p_wild_bertrand2         = price_trader(price_poachers_bertrand2, a_f, a_w, b_f, b_w, e, c),
                           profit_farmed_bertrand2  = profit_farm(p_wild_bertrand2, p_farmed_bertrand2, a_f, b_f, e, v),
                           profit_trader_bertrand2  = profit_trader(p_wild_bertrand2, p_farmed_bertrand2, a_w, b_w, e, price_poachers_bertrand2, c),
                           #Third steady state : 
                           price_poachers_bertrand3 = s_b_own(ss_bertrand3, a_f, a_w, b_f, b_w, e, W, c),
                           farmed_bertrand3         = quantity_farmed(price_poachers_bertrand3, a_f, a_w, b_f, b_w, e, W, c),
                           p_farmed_bertrand3       = price_farmed(price_poachers_bertrand3, a_f, a_w, b_f, b_w, e, c),
                           p_wild_bertrand3         = price_trader(price_poachers_bertrand3, a_f, a_w, b_f, b_w, e, c),
                           profit_farmed_bertrand3  = profit_farm(p_wild_bertrand3, p_farmed_bertrand3, a_f, b_f, e, v),
                           profit_trader_bertrand3  = profit_trader(p_wild_bertrand3, p_farmed_bertrand3, a_w, b_w, e, price_poachers_bertrand3, c))
  
    store['transformation'] = as.character(store$transformation)
  
    write.csv(store, here('data', 'sensitivity_steady_states_last.csv'), row.names = F)

    }
  else{
    numcores = detectCores() - 4
# Set up storage
    store = data.frame()

# Set up the width of each run
    width = nrow(params_sensitivity)
    number_op = nrow(params_sensitivity)/width

# Loop over several runs is faster than 1 big run
    for (x in 1:number_op){
    # Make clusters
      cl = makeCluster(numcores)
    # Load tidyverse : otherwise, pipe operator is not recognized
      clusterEvalQ(cl,  library(tidyverse))

    # Start timer
      start = Sys.time()
    # Apply function accross nodes with a slice of the data of lenght width
      a = parApply(cl, 
                   params_sensitivity[width*(x-1)+1:width*x,],
                   1,
                   run_model_par)
      print(Sys.time() - start)

      a = as.data.frame(a)

      store = rbind(store, t(a))
    }
    colnames(store) = c('k', 'sigma', 'W', 'beta', 
                        'gamma_primitive', 'v', 'c', 
                        'alpha', 'r', 'gamma','ss_monop1', 'ss_monop2', 'ss_monop3',
                        'ss_cournot1', 'ss_cournot2', 'ss_cournot3', 'ss_bertrand1', 
                        'ss_bertrand2', 'ss_bertrand3')
  
    write.csv(store, here('data', 'sensitivity_steady_states_last.csv'), row.names = F)
}
}else{
  store = read.csv(here('data','sensitivity_steady_states_last.csv'))
}

```

For example : 

```{r}
to_long = colnames(store)
to_long = to_long[12:length(to_long)]

a = store %>% 
  pivot_longer(cols = to_long, 
               names_to = 'output',
               values_to = 'value')
head(a)
```

I have an issue with the best way to plot data. I think using a long format is better to use the functionalities from `ggplot2`. I think there's still one more round of analysis to do : for each different value of `spec` and `transformation`, we need to find the value that maximizes the profit of the aquaculture firm. Then, I think it should be ok to use a long format to plot the data. 

```{r}

ggplot(a, aes(x=transformation, y=value, color=transformation)) +
  geom_line()
```